Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-05-15 hazelnut-popl17.tex
clarification of why the premise in one of the rules for application actions makes sense

If the focused empty hole is being analyzed against a type that is incompatible with an arrow type, then a lambda ascribed the type $\tarr{\tehole}{\tehole}$ is inserted inside a hole, to maintain Theorem \ref{thrm:actsafe}:
\begin{equation}
  \inferrule{
    \tincompat{\htau}{\tarr{\tehole}{\tehole}}
  }{
    \performAna
      {\hGamma}
      {\zwsel{\hehole}}
      {\htau}
      {\aConstruct{\flam{x}}}
      {\hhole{
        \hlam{x}{\hehole} : \tarr{\zwsel{\tehole}}{\tehole}
      }}
  }
\end{equation}

>>>>

If the focused empty hole is being analyzed against a type that is
incompatible with any arrow type, expressed in the premise as an arrow with
two holes, then a lambda ascribed the type $\tarr{\tehole}{\tehole}$
is inserted inside a hole, to maintain Theorem \ref{thrm:actsafe}:
\begin{equation}
  \inferrule{
    \tincompat{\htau}{\tarr{\tehole}{\tehole}}
  }{
    \performAna
      {\hGamma}
      {\zwsel{\hehole}}
      {\htau}
      {\aConstruct{\flam{x}}}
      {\hhole{
        \hlam{x}{\hehole} : \tarr{\zwsel{\tehole}}{\tehole}
      }}
  }
\end{equation}
